\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace,microtype}
\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage{siunitx}
\setstretch{1.15}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\pagestyle{empty}
\input{auto/v4_publication_numbers.tex}

\begin{document}

\begin{center}
{\large\bfseries Executive Summary}\\[0.35em]
{\normalsize Simultaneous Group-Envelope Bounds for $\Gamma$-Robust Multiple-Choice Knapsack Problems}\\[0.35em]
{\small July 2026}
\end{center}

Many resource-allocation decisions choose exactly one option per group.  Protecting their shared constraint with a Bertsimas--Sim uncertainty budget produces a robust multiple-choice knapsack problem.  The classical threshold reduction is polynomial, but a large set of distinct deviations can make complete relaxation certification expensive.

After dualizing the capacity constraint of a fixed-threshold MCKP, all threshold-dependent baselines cancel.  Between consecutive deviations in a group, the remaining envelope is the maximum of one constant and one common-slope line.  Prefix and suffix maxima with range accumulation evaluate one multiplier over all $B$ thresholds in $O(B+K\log(B+1))$ time and $O(B+K)$ working storage, rather than $\Theta(BK)$ direct score evaluations, for $K$ options.

Weak duality makes the interval minimax value a valid upper bound on every feasible fixed-threshold LP in the interval; strong LP duality gives equality on feasible singleton intervals.  A new epigraph-dual mapping proves that the exact minimax envelope bound is no larger than the bounded-threshold group-clique LP.  Convex geometric bracketing and Lipschitz contraction return an evaluated valid bound together with an explicit minimization-error certificate.  A best-first splitting algorithm then certifies the maximum LP value over the complete threshold family to a requested scaled tolerance.

The complete protocol and gates are serialized with the release.  Across \PubPrimaryCases{} primary instances, the compressed certificate reaches scaled tolerance $10^{-6}$ throughout, wins all \PubPrimaryWins{} paired timings, and is \PubPrimaryGeoSpeedup{} times faster in geometric mean than a sparse bounded-threshold group-clique LP (95\% design-stratified bootstrap interval \PubPrimaryCILow--\PubPrimaryCIHigh).  Speedup increases from \PubPrimaryNLowSpeedup{} at 360 groups to \PubPrimaryNHighSpeedup{} at 1,440 groups.  All 36 robustness cases reach tolerance.  A transparent two-option transformation of \PubExternalCases{} published robust-knapsack coefficient sets wins \PubExternalWins{} timings with a \PubExternalGeoSpeedup-fold advantage; it is an out-of-generator stress test, not a replication of the source uncertainty model.  Independent algebraic, epigraph-LP, and exhaustive-scan checks find maximum error \PubValidationMaxError, with maximum scaled multiplier-certificate gap \PubValidationCertGap.

The released implementation also embeds either interval bound in an exact integer threshold search.  A separate audit confirms objective agreement and valid gap accounting, while showing that integer subproblem work can erase the oracle advantage and that compact SCIP remains preferable on many-breakpoints instances.  The analysis therefore concerns simultaneous all-threshold Lagrangian evaluation for exactly-one groups, not the classical threshold reduction, a new robust formulation, or universal integer-solver superiority.

\end{document}
